---
title: "CMA - Exercise week 4"
author: "Dionis Anderegg"
date: "21 Mai 2021"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

## Using Functions

Create a test-function and run it:
```{r}
testfun <- function () {}
testfun()         # NULL as this function doesn't give an output
class(testfun)    # It is an element of class "function"
```

How to specify what the function does (use {})
```{r}
testfun <- function () {print("this function does nothing")}
testfun()

my_age <- function(birthday, units) {
  difftime(Sys.time(), birthday, units = units)
}
my_age("1991-11-16", units = "days")

# Use default values:
my_age <- function(birthday, units = "days") {
  difftime(Sys.time(), birthday, units = units)
}
my_age("1991-11-16")
my_age("1991-11-16", units = "hours")   # Still, other units than default are possible.
```

## Task 1: Write your own functions
Creating a function to taoculate the euclidian distance
```{r}
euclidian_dist <- function(E.x, E.y, N.x, N.y) {
  sqrt((E.x-E.y)^2 + (N.x-N.y)^2)
}
euclidian_dist_lead <- function(E, N) {
  sqrt((E-lead(E))^2 + (N-lead(N))^2)
}
```

## Task2: Prepare the analysis
Import Dataset and filter it:
We will only Use the individuals Rosa and Sabi for the timespan of 01.04.2015 - 15.04.2015
```{r}
raw <- read_delim("wildschwein_BE_2056.csv", delim = ",")
summary(raw)

data.filter <- raw %>%
  filter(TierName == "Sabi" | TierName =="Rosa", 
         DatetimeUTC >= as.POSIXct("2015-04-01", tz = "UTC"), 
         DatetimeUTC <= as.POSIXct("2015-04-15", tz = "UTC"))
```

## Task 3: Create join key
Crate a rouded data for every 15 minutes => This will be the join key.
```{r}
data.filter$DatetimeUTC <- round_date(data.filter$DatetimeUTC, unit = "15 minutes")
```


## Task 4: Measuring distance at cuncurrent locations
Create two datasets (one per animal), and join the datasets by DateTimeUTC.
Calculate the euclidian distance between the two individuals, using the previously definded function.
```{r}
data.filter.sabi <- filter(data.filter, TierName == "Sabi")
data.filter.rosa <- filter(data.filter, TierName == "Rosa")

data.join <- left_join(data.filter.sabi, data.filter.rosa, by = "DatetimeUTC", suffix = c("Sabi", "Rosa"))
data.join$distance <- euclidian_dist(data.join$ESabi, data.join$ERosa, data.join$NSabi, data.join$NRosa)
data.join$meeting <- ifelse(data.join$distance <=100, TRUE, FALSE)

# Filter and gather the relevant data for visuailzation:
data.join.vis %>%
  select(DatetimeUTC, ERosa, NRosa, ESabi, NSabi, distance) +
  gather()
```

## Task 5: Visualize Data
```{r}
ggplot(filter(data.join, distance < 3000)) +
  geom_point(aes(ERosa, NRosa), col = "red",alpha = 0.1) +
  geom_point(aes(ESabi, NSabi), col = "blue", alpha = 0.1) +
  geom_point(aes(ERosa, NRosa, alpha = meeting), col = "black") +
  labs() +
  theme_bw()
```


